Efficiently stable presentations from error-correcting codes

### 2025-10-21 daj-revision2/referee-response.txt

I am not fully happy with the revision. Most of my comments and suggestions
 have been taken into account, but not all. Several have been ignored for a
good reason (14 15 20 were completely wrong and 7 was perhaps not relevant),
but it seems that the authors have not got what I meant in my comments 34
and 35.

@@

In 34, I was just asking that you explain in the text of your paper how
Corollary 5.12 improves Theorem 7.14 in [JNV+20a]. What you wrote The
statement is stronger than Theorem 7.14 in [JNV+20a], which involves a game
that has a question with long answers is exactly the kind of thing I was asking.
Would you agree to add it to the text?

A: Ok, we added a sentence right before the statement of Corollary 5.12

In 35, I was just suggesting a different way of phrasing your proof. I guess
that I was implicitely complaining that you were reproducing again the same
argument that you had written many times earlier (and that I called “Lemma 1”
in my first report). And that it would be kind to the reader if you encapsulated
the idea as a lemma so that you can only refer to it each time you use it. Now
that you did it in you new Lemma 2.7, you’d better use it rather than reproving
it. See 21 below.

A: See response to 21 below. Unfortunately at this point we feel that we are getting lost in trying to follow the reviewer's desire to rewrite our proof, and would prefer to stop there--see below.

@@

More importantly, the comments 9 10 13 14 19 21 have not been fully ad-
dressed, or resulted in adding new inaccuracies (see points 2–5, 8, 7, 10, 18). In
particular I fully disagree with your reply to 21, see point 18 below.
Here are some comments. Some are new and some are about previous com-
ments.

1. page 9, Definition 2.4. You made the choice to only discuss what is usually
called flexible stability and not the more restrictive notion where you do
not change de dimension/algebra of the representation. This choice is
understandable because flexible stability is much more common that non-
flexible stability, but maybe it’s worth pointing out the stability results
that are true for the stronger form of non-flexible stability. In particular,
this seems to be the case for Theorem 4.1. This deserves to be written.

A: We added a remark right after Definition 2.4 to point to the relevant literature. For our paper, we prefer to use the definition we give and not include comparisons everywhere.

2. page 9, Claim 2.3. There are squares missing. (3) is certainly correct
(perhaps with a different constant than 3), but I did not follow, in the
proof, how you take into account the renormalization of the trace on N .
[...]

A: Thanks, you are correct. Actually the claim was not used so we removed it.

@@

15. page 25, Claim 4.2: do you need Claim 4.2? Corollary 2.15 that you use
later does not require that ϕ takes its values in the hermitian unitaries.

A: You're right, these relations are supserseded by the "Hadamard" relations and were not necessary. We removed them from the presentation, removed Claim 4.2, and adapted the rest of the text.

16. page 26, Claim 4.4: why the √ε? Claim 4.3 exactly says that ϕ is
(δ, μS )-close to U with δ = O(ε), and Lemma 2.7 (or its proof) says that
E∥[Uu,α, Uv,α′ ] − [ϕ(su,α), ϕ(sv,α′ )]∥2 ≤ 16δ for any probability measure
on pairs whose marginals are μS .

A: Yes this was a typo in the last line of the proof, we corrected it.

@@

17. page 28, line 3: what you write is not true for a fixed u, but it is true on
average over u.

A: Corrected

18. page 29, line -5– -1: the conventions for the notation poly here (given
in footnote 7) do not match those of [JNV+22]. For example, on the
last line of page 23 of [JNV+22], you have an expression of the form
poly(ε, n−1) + e−Ω(r/m2) that becomes, in the conclusion of [JNV+22,
Theorem 4.1] poly(ε, n−1, e−Ω(r/m2)). And similarly all over [JNV+22].
So, the way you prove Theorem 4.1 has two problems: (a) you do not
prove that the presentation given in (22) is stable in the sense of Definition
1.2 (because you do not prove limε δ(ε) = 0) and (2) your convention of
poly contradicts your use of it.
When you write Yes, we are sure that the modulus goes to 0 with epsilon,
I agree that this is true, but where is it proven? I did not find the proof
written, neither in [JNV+22] nor in your submission. I thought that what
is proven in [JNV+22] is with δ(ε) ≤ C(mC + dC )(ε1/C + q−1/C ) for some
universal C, which is C(mC + dC )q−1/C > 0 for ε = 0.
If you want to stick to the convention that limε δ(ε) = 0, one cheap way is
to exploit Lemma 2.6 and [GH17] to explain that the modulus of stabil-
ity in Theorem 4.1 is something like min(C1ε, C2poly(ε, 1/q)) for a good
(=polynomial in the parameters) constant C2 and a bad (=exponential in
the parameters) constant C1.

A: You're right, we were overly sloppy there. Yes, your interpretation of the poly() notation is correct and we made a mistake in translating it. This has been corrected. We changed the bound in the theorem to have a bound that goes to 0 with eps, as required (by employing a min) and slightly edited the discussion that follows the statement of the theorem.

@@

A: If the constant implicit in the Omega(.) is at least 12, the condition is satisfied? We thought this should be clear.

20. page 29, line -1: you could explain why the existence of Gc implies the
conclusion of the theorem: write the homomorphism that is δ(ε)-close to

A: We added it.

21. Here is what I had in mind in my comment 35. [...]

A: We prefer not to follow the referee's suggestion. To prove a lower bound on the modulus of stability, we need to find a \eps-almost representation which is **far** from all actual representations. In our case, this is done in two Claims --- A2 and A3. Claim A2 shows that some given function is an \eps-almost representation, and Claim A3 shows that this function is far from any actual representation. The referee's general lemma is nice, but in the application to the present situation they seem to claim to find a presentation of F_2^n which uses n generators and only 3n/2 relations (the order 2 relations + commutation of a perfect matching). This is not a presentation of F_2^n, but the free product of n/2 copies of F_2^2. We do not see an easy way of using his lemma to prove our claim. Since we have a proof that works we prefer to stay with it.

### 2025-10-21 daj-revision2/efficient_stability.tex
final referee edits

Regarding this definition, we state the following elementary claim. \tnote{added this, which seems useful; I'm surprised we didn't need it before?}\tnote{I fixed the claim but actually I don't think it is needed..}

\begin{claim}
Suppose that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close. Then the following hold, where $C$ is a universal constant:
\begin{align}
\Es{i\sim \mu} \| wU_i w^* - V_i \|_{\tau^\mN}^2 &\leq C\delta\;,\label{eq:switch-w}\\
\Es{i\sim \mu} \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM}^2 &\leq \delta\;. \label{eq:switch-inv}
\end{align}
\end{claim}

\begin{proof}
We first note that by definition
\begin{align*} 
1\geq \tau^\mN(ww^*)  
&= \frac{1}{\tau_\infty(P)}\tau_\infty(ww^*) \\
&= \frac{1}{\tau_\infty(P)}\tau^\mM(w^*w)  \\
&\geq \frac{1}{\tau_\infty(P)}(\tau^\mM(I_\mM)-\delta)\;, 
\end{align*}
from which it follows that $\tau_\infty(P)\geq 1-\delta$.
Now for the first inequality, for any $i$ we have by the triangle inequality 
\begin{align*}
  \| wU_i w^* - V_i \|_{\tau^\mN} &\leq \| w U_i w^* - w w^* V_i w w^* \|_{\tau^\mN} + \|(P-ww^*)V_i ww^* \|_{\tau^\mN} + \|V_i(P-ww^*)\|_{\tau^\mN}\\
  &\leq \frac{1}{\tau_\infty(P)}\| U_i - w^* V_i w\|_{\tau^\mM} + 2 \|(P-ww^*)\|_{\tau^\mN}\\
	&\leq \frac{1}{1-\delta}\| U_i - w^* V_i w\|_{\tau^\mM} + 2\delta \;,
\end{align*}
where the second line uses that $w^*$ is a partial isometry. Eq.~\eqref{eq:switch-w} follows. For the second inequality, for any $i$,
\begin{align*}
  \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &=  \| (U_i^{-1} - w^* V_i^{-1} w)^* \|_{\tau^\mM}\\
	%\| 1_\mM -  U_i w^* V_i^{-1} w \|_{\tau^\mM}\\
  %&\leq \|w^* w - w^* w U_i w^* V_i^{-1} w \|_{\tau^\mM} + \|w^*w-1_\mM\|_{\tau^\mM} \\
%&\leq \|P - wU_iw^* V_i^{-1}\|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \\
&= \|U_i - w^* V_i^{-1} w \|_{\tau^\mN} \;, %+ \|w^*w-1_\mM\|_{\tau^\mM} \;,
\end{align*}
%where the first inequality is the triangle inequality and the second uses that $w$ is a partial isometry. 
since $U_i$ and $V_i$ are unitaries. 
%We conclude by taking the average over $i\sim \mu$ and applying~\eqref{eq:switch-w}.
\end{proof}

@@

@@

\tnote{Maybe we should cut the end of the section, starting from here? It seems that the informal discussion would be enough, and the formal claim does not seem to be used. In particular, the tester is basically redefined in Figure~\ref{fig:bRM-tester}. So we could just write that we spell things out there.}
More precisely, define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where 
\begin{itemize}
	\item $A \in \F_2^{nq^2 \times nq}$ is itself a block-diagonal matrix where the diagonal blocks are the $q^2 \times q$ parity check matrix for the Hadamard code. 
	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{q^2 \times q}$ is the parity check matrix for the Hadamard code. 
	\item $B \in \F_2^{\ell q \times nq}$, where $\ell$ is the number of rows of $h$, is viewed as having rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$. The entry in row $(p,\gamma)$ and column $(i,x)$ is $1$ if and only if $h_{pi} \neq 0$ and $x = \kappa(\gamma h_{pi})$.
\end{itemize}
Define the distribution $\nu'$ as the uniform mixture of the uniform distribution on the rows of the $A$ block matrix and the uniform distribution on the rows of the $B$ block matrix.

@@

\begin{theorem}\label{thm:z2-stab}
Let $\mC$ be the class of all tracial von Neumann algebras. 
The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with \tnote{edited, referee did not like $\poly$}$\delta(\eps)= C (mdt)^{c_1} (\eps/q)^{c_2}$, where $C,c_1,c_2$ are universal positive constants.  
\end{theorem}

We briefly explain a possible setting of parameters in Theorem~\ref{thm:z2-stab}. For any integer $t\geq 1$, fix $q=2^t$ and let $d=m=c t^c$ for some constant $c>0$. Then $k=t(d+1)^m = 2^{\Theta((\log q)^c \log\log q)}$ and $N=q^{m+1}= 2^{\Theta((\log q)^{c+1} \log\log q)}$. Moreover, the number of relations in~\eqref{eq:z2k-eff} is $O(N^2)$, which scales as $2^{\poly\log k}$; and the maximum length of a relation is $d+2=O(\log k)$. Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\poly(\log k)\cdot \poly(\eps)$. We have thus obtained a presentation of $\Z_2^k$ of size only mildly superpolynomial in $k$, and with soundness that depends polylogarithmically on $k$.

\begin{proof}
Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $(\eps,\mu_S)$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
 Here, $S = \{s_{u,a}: u\in (\F_2^t)^m, a\in \F_2^t\}$. We sometimes enumerate the items of $S$ as $S=\{x_i: i\in\{1,\ldots,N\}\}$, where $N=2^{tm+t}$ and we fixed an arbitrary bijection between $(\F_2^t)^m\times \F_2^t$ and $\{1,\ldots,N\}$. Let $R$ be the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R=  \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.

The proof strategy is to perform a reduction to~\cite[Theorem 4.1]{ji2022quantum}. Towards this, the main technical work in the proof consists in using the unitaries $\phi(s_{u,a})$ in order to define a synchronous strategy in the tensor code test from~\cite{ji2022quantum}, where the underlying code is the Reed-Solomon code with degree $d$ over $\F_q$. To define the synchronous strategy, we need ``points,'' ``lines,'' and ``pair'' measurements (see~\cite{ji2022quantum} for the terminology). Each of these is a family of projective measurements that obey certain constraints.

@@

We are now in a position to apply~\cite[Theorem 4.1]{ji2022quantum}. For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ considered in Section~\ref{sec:rmq} (see the remark right after Lemma~\ref{lem:schwartz-zippel}). For the ``points measurement'' $A^u$ we choose $P^u$. For the ``lines measurement'' $B^\ell$ we choose $Q^\ell$ from Claim~\ref{claim:z2-stab-4}. Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}. By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that for all integers $r \geq 12mt$,
\[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.

@@

In the next section we detail an important application of this test, Proposition~\ref{prop:dim-test}, which is used in the work~\cite{ji2020mip}. (The present proof somewhat simplifies the one given in~\cite{ji2020mip}, but it keeps the same overall strategy. \tnote{added for revision 2:}We also note that Corollary~\ref{cor:qld} below is qualitatively stronger than~\cite[Theorem 7.14]{ji2020mip} as the latter applies to a slightly different game which in particular has a pair of questions with long answers, of $O(2^m\log q)$ bits, whereas the tester in Figure~\ref{fig:bRM-tester}, which is analysed in the corollary, has short answers, $O(d)$ bits long. The presence of long answers helps the analysis.)

>>>>

%Regarding this definition, we state the following elementary claim. \tnote{added this, which seems useful; I'm surprised we didn't need it before?}\tnote{I fixed the claim but actually I don't think it is needed..}
%
%\begin{claim}
%Suppose that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close. Then the following hold, where $C$ is a universal constant:
%\begin{align}
%\Es{i\sim \mu} \| wU_i w^* - V_i \|_{\tau^\mN}^2 &\leq C\delta\;,\label{eq:switch-w}\\
%\Es{i\sim \mu} \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM}^2 &\leq \delta\;. \label{eq:switch-inv}
%\end{align}
%\end{claim}
%
%\begin{proof}
%We first note that by definition
%\begin{align*} 
%1\geq \tau^\mN(ww^*)  
%&= \frac{1}{\tau_\infty(P)}\tau_\infty(ww^*) \\
%&= \frac{1}{\tau_\infty(P)}\tau^\mM(w^*w)  \\
%&\geq \frac{1}{\tau_\infty(P)}(\tau^\mM(I_\mM)-\delta)\;, 
%\end{align*}
%from which it follows that $\tau_\infty(P)\geq 1-\delta$.
%Now for the first inequality, for any $i$ we have by the triangle inequality 
%\begin{align*}
  %\| wU_i w^* - V_i \|_{\tau^\mN} &\leq \| w U_i w^* - w w^* V_i w w^* \|_{\tau^\mN} + \|(P-ww^*)V_i ww^* \|_{\tau^\mN} + \|V_i(P-ww^*)\|_{\tau^\mN}\\
  %&\leq \frac{1}{\tau_\infty(P)}\| U_i - w^* V_i w\|_{\tau^\mM} + 2 \|(P-ww^*)\|_{\tau^\mN}\\
	%&\leq \frac{1}{1-\delta}\| U_i - w^* V_i w\|_{\tau^\mM} + 2\delta \;,
%\end{align*}
%where the second line uses that $w^*$ is a partial isometry. Eq.~\eqref{eq:switch-w} follows. For the second inequality, for any $i$,
%\begin{align*}
  %\| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &=  \| (U_i^{-1} - w^* V_i^{-1} w)^* \|_{\tau^\mM}\\
	%%\| 1_\mM -  U_i w^* V_i^{-1} w \|_{\tau^\mM}\\
  %%&\leq \|w^* w - w^* w U_i w^* V_i^{-1} w \|_{\tau^\mM} + \|w^*w-1_\mM\|_{\tau^\mM} \\
%%&\leq \|P - wU_iw^* V_i^{-1}\|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \\
%&= \|U_i - w^* V_i^{-1} w \|_{\tau^\mN} \;, %+ \|w^*w-1_\mM\|_{\tau^\mM} \;,
%\end{align*}
%%where the first inequality is the triangle inequality and the second uses that $w$ is a partial isometry. 
%since $U_i$ and $V_i$ are unitaries. 
%%We conclude by taking the average over $i\sim \mu$ and applying~\eqref{eq:switch-w}.
%\end{proof}

@@

\begin{remark}
    Definition \ref{def:eff-stab} is often referred to in the literature as ``flexible pointwise Hilbert--Schmidt stability (in the class $\mC$)''. There are other versions of stability, such as: the non-flexible one (cf.\ \cite{becker2019stability, hadwin2018stability}), in which one does not allow to compare representations of different dimensions; uniform stability, in which almost representations are with respect to  the (often) infinite multiplication table presentation (cf.\ \cite{kazhdan1982e,becker2022stability}); stability in permutations, where instead of studying approximate representations one studies approximate actions (cf.\ \cite{becker2019stability,becker2020group, ioana2020stability}); and so on. In the cited papers above there are thorough literature surveys that we avoid herein.
\end{remark}

@@

More precisely, define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where 
\begin{itemize}
	\item $A \in \F_2^{nq^2 \times nq}$ is itself a block-diagonal matrix where the diagonal blocks are the $q^2 \times q$ parity check matrix for the Hadamard code. 
	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{q^2 \times q}$ is the parity check matrix for the Hadamard code. 
	\item $B \in \F_2^{\ell q \times nq}$, where $\ell$ is the number of rows of $h$, is viewed as having rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$. The entry in row $(p,\gamma)$ and column $(i,x)$ is $1$ if and only if $h_{pi} \neq 0$ and $x = \kappa(\gamma h_{pi})$.
\end{itemize}
Define the distribution $\nu'$ as the uniform mixture of the uniform distribution on the rows of the $A$ block matrix and the uniform distribution on the rows of the $B$ block matrix.

@@

\begin{theorem}\label{thm:z2-stab}
Let $\mC$ be the class of all tracial von Neumann algebras. 
The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with 
\begin{equation}\label{eq:th-min}
 \delta(\eps) = \min\Big\{ C (mdt)^{c_1} (\eps^{c_2}+(1/q)^{c_3})\ ,\ C'_{t,d,m}\ \eps\Big\}\;,
\end{equation}
where $C,c_1,c_2,c_3$ are universal positive constants and $C'_{t,d,m}$ depends on $t,d,m$ but not $\eps$.\footnote{We do not attempt to compute the dependence of $C'_{t,d,m}$ on the parameters because we are more interested in the regime of parameters where the first part of the min is relevant. Nevertheless, we include it so that $\delta(\eps)\to_{\eps\to 0} 0$, as required.}   
\end{theorem}

We briefly explain a possible setting of parameters in Theorem~\ref{thm:z2-stab}. For any integer $t\geq 1$, fix $q=2^t$ and let $d=m=c t^c$ for some constant $c>0$. Then $k=t(d+1)^m = 2^{\Theta((\log q)^c \log\log q)}$ and $N=q^{m+1}= 2^{\Theta((\log q)^{c+1} \log\log q)}$. Moreover, the number of relations in~\eqref{eq:z2k-eff} is $O(N^2)$, which scales as $2^{\poly\log k}$; and the maximum length of a relation is $d+2=O(\log k)$. Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\min\{ \poly(\log k)\cdot (\poly(\eps) + \poly(1/k)),C'_k\eps\}$. When $\eps$ is much larger than $1/k$, the first term in the $\min$ scales as $\poly(\log k)\cdot \poly(\eps)$, which gives a favorable tradeoff between the presentation size and the modulus of stability. For very small $\eps$, the bound is what we would generically expect from Theorem~\ref{thm:gh} and the size of the presentation ; in particular the constant $C'_k$ necessarily scales exponentially with $k$.

\begin{proof}
Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $(\eps,\mu_R)$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
 Here, $S = \{s_{u,a}: u\in (\F_2^t)^m, a\in \F_2^t\}$. We sometimes enumerate the items of $S$ as $S=\{x_i: i\in\{1,\ldots,N\}\}$, where $N=2^{tm+t}$ and we fixed an arbitrary bijection between $(\F_2^t)^m\times \F_2^t$ and $\{1,\ldots,N\}$. Let $R$ be the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R=  \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.

The second bound in the $\min$ in~\eqref{eq:th-min} follows immediately from Theorem~\ref{thm:gh} and Lemma~\ref{lem:stab-group} according to Remark~\ref{rk:linear-modulus}. Therefore, the bulk of the proof focuses on establishing the first bound. 
The proof strategy is to perform a reduction to~\cite[Theorem 4.1]{ji2022quantum}. Towards this, the main technical work in the proof consists in using the unitaries $\phi(s_{u,a})$ in order to define a synchronous strategy in the tensor code test from~\cite{ji2022quantum}, where the underlying code is the Reed-Solomon code with degree $d$ over $\F_q$. To define the synchronous strategy, we need ``points,'' ``lines,'' and ``pair'' measurements (see~\cite{ji2022quantum} for the terminology). Each of these is a family of projective measurements that obey certain constraints.

@@

We are now in a position to apply~\cite[Theorem 4.1]{ji2022quantum}. For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ considered in Section~\ref{sec:rmq} (see the remark right after Lemma~\ref{lem:schwartz-zippel}). For the ``points measurement'' $A^u$ we choose $P^u$. For the ``lines measurement'' $B^\ell$ we choose $Q^\ell$ from Claim~\ref{claim:z2-stab-4}. Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}. By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that for all integers $r \geq 12mt$,
\begin{equation}\label{eq:41-last}
 \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,
\end{equation}
where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$. The first bound in the $\min$ in~\eqref{eq:th-min} then follows where explicitly, the homomorphism that is close to $\phi$ is given by
\[ g: s_{u,a} \mapsto \sum_{\beta\in\F_q} (-1)^{a\cdot \kappa(\beta)} \sum_{c:\ c(u)=\beta} G_c \;,\]
and closeness follows from~\eqref{eq:41-last} and~\eqref{eq:z2-stab-2} by expanding the square in the definition.
 %It suffices to verify that the constant implicit in the $O(\eps)$ in Remark~\ref{rk:linear-modulus} is of order $\poly(|\mathbb{Z}_2^k|)=2^{O(k)}$. 
\end{proof}

@@

In the next section we detail an important application of this test, Proposition~\ref{prop:dim-test}, which is used in the work~\cite{ji2020mip}. The present proof somewhat simplifies the one given in~\cite{ji2020mip}, but it keeps the same overall strategy. \tnote{added for revision 2:}Moreover, Corollary~\ref{cor:qld} below is qualitatively stronger than~\cite[Theorem 7.14]{ji2020mip} as the latter applies to a slightly different game which in particular has a pair of questions with long answers, of $O(2^m\log q)$ bits, whereas the tester in Figure~\ref{fig:bRM-tester}, which is analyzed in the corollary, has short answers, $O(d)$ bits long; with a typical parameter setting (see the discussion following Theorem~\ref{thm:z2-stab}) this is exponentially smaller. The presence of long answers makes the analysis easier.
